Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-11-07 doc/gaia-chapter.tex
minor changes
add a lemma; small change in gaia-chapter.tex

\section{Gaia's proof of well-foundedness}
The library \texttt{gaia-hydras} already contains two proofs
of well-foundedness of the strict order on ordinal terms in
Cantor normal form: a direct proof~\vref{sec:T1Wf} and a proof based on the recursive path ordering~\vref{remark:a3pat}, by
\'Evelyne Contejean. We found it interesting to comment Gaia's proof, which uses tools already present in~\cite{CantorContrib}.

@@

%\inputsnippets{nfwfgaia/haveHc}

>>>>

\section{Gaia's proof of well-foundedness}
The library \Hydras already contains two proofs
of well-foundedness of the strict order on ordinal terms in
Cantor normal form: a direct proof~\vref{sec:T1Wf} and a proof based on the recursive path ordering~\vref{remark:a3pat}, by
\'Evelyne Contejean. We found it interesting to comment Gaia's proof, which uses tools already present in~\cite{CantorContrib}.

@@

By the following two forward steps, we show that $b$ is accessible, and will be able to prove properties by induction on $b$'s accessibility.

\inputsnippets{nfwfgaia/haveHc}
